\chapter*{Abstract}
\label{chap:abstract}
\addcontentsline{toc}{chapter}{\nameref{chap:abstract}}

For campuses, food choices and their availability are an important aspect for students,
and in order to cover all their preferences, there is a high chance that food choices will overwhelm students.
The motivation of this project is to simplify the decision-making process for students in choosing meals from
various food stalls within the cafeterias at Kasetsart University so they can save time and enjoy their meal.
Our project “KU Eater” addresses the lack of a centralized data source for menu items being offered in cafeterias and stall locations,
as the aforementioned data is not available in a consolidated digital format. Cafeterias may offer an abundance of choices for food,
but without any personalized guidance, this can lead to potential dissatisfaction with meals.
KU Eater proposes a solution to the problems by being a web-based application with features combatting the challenges of this project:
AI-based personalized food stall recommendation, in-depth dish name search and food stall review.
The effectiveness of the KU Eater project is evaluated through application analytics and user feedback.
We expect our project's effects to include an improvement in students' satisfaction with their meal choices.
We believe that tailored meal choices may bring more positivity to students on university grounds.
\par
\textit{\textbf{Keywords}---Educational Institutions, Web Application, Recommendation Systems, Machine Learning, Natural Language Processing}