\newcounter{nuserstory}
\newcommand{\userstory}[4]{%
    \refstepcounter{nuserstory}
    \subsection{#1}
    \label{userstory:\thenuserstory}
    \hangindent=40pt
    \textbf{\textit{As a}} #2,\\
    \textbf{\textit{I want to}} #3,\\
    \textbf{\textit{so that}} #4.
}

% With user stories (\userstory) you can reference them back later with \ref{userstory:n}
% For example, first user story in this file can be referred with \ref{userstory:1}

\chapter{Requirement Analysis}
\label{chap:requirement-analysis}

\section{Stakeholder Analysis}
\label{section:stakeholder-analysis}

\subsection{Primary Stakeholders}
\label{subsection:primary-stakeholders}

\begin{enumerate}[leftmargin=80pt]
    \item \textbf{Users:} The primary stakeholders are users of our application,
    they have a key role to populate our application's data, and evaluate our project's impact.
    For specification of our users see \ref{section:target-user}.
    \item \textbf{Food stall owners:} Owners of food stalls in cafeterias on Kasetsart University grounds
    is our primary source of data acquisition. With KU Eater, we make sure to bring positive changes not just to
    consumers but also the producers.
\end{enumerate}

\section{User Stories}
\label{section:user-stories}

\userstory{%
    User Story Title%
}{%
    who%
}{%
    what%
}{%
    why%
}

\section{Use Case Diagram}
\label{section:use-case-diagram}
<TIP: Write a use case diagram for your project here. Refer to an
article “What is a use case diagram?” by Lucidchart for help./>

\section{Use Case Model}
\label{section:use-case-model}
A use case is a detailed description of how a system
interacts with an external entity (such as a user or another system) to
accomplish a specific goal. Use cases provide a high-level view of the
functionality of a system and help in capturing and documenting its
requirements from the perspective of end users.

<TIP: Write use cases for your project here. Make sure to use the
appropriate type of use case for each scenario (brief, casual, and fully-dressed
use case)./>

\section{User Interface Design}
\label{section:user-interface-design}
<TIP: Put the initial design of your application here. You can
showcase a detailed design of a specific page or a sitemap of your application.
See an example below./>